KV Analysis for Performing-Dynamics performances

### 2020-05-20 material/analysis/expression/stim_d/kv.Rmd
export valid trials
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Analysis for Performing-Dynamics performances (Key Velocity)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance from teaching-v2.0 (KV).

@@

@@

p_kv_seq_for <- ggplot(data = kv_seq_for, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Key Velocity") + scale_x_continuous(breaks=seq(1,66,1))
p_kv_seq_for
```

@@

p_kv_seq_pia <- ggplot(data = kv_seq_pia, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Key Velocity") + scale_x_continuous(breaks=seq(1,66,1))
p_kv_seq_pia
```

@@

```{r kv_dis_for, fig.width = 14, fig.height = 8, echo = FALSE}
p_kv_dis_for <- ggplot(dt_kv[Subcomponent == "Forte"], aes(x = Velocity)) +
  geom_histogram(binwidth = 2, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Key Velocity", y = "Count", subtitle = "KV: Performing-Dynamics(Forte)")
p_kv_dis_for
```

```{r kv_dis_pia, fig.width = 14, fig.height = 8, echo = FALSE}
p_kv_dis_pia <- ggplot(dt_kv[Subcomponent == "Piano"], aes(x = Velocity)) +
  geom_histogram(binwidth = 2, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Key Velocity", y = "Count", subtitle = "KV: Performing-Dynamics(Piano)")
p_kv_dis_pia
```

@@

### Exclude outlier participants
#### Forte
```{r outlier_for, echo = FALSE}
# for forte
excluded_duration_for <- kv[Subcomponent == "Forte" & Mean < kv_all[Subcomponent == "Forte"]$Mean+3*kv_all[Subcomponent == "Forte"]$SD & Mean > kv_all[Subcomponent == "Forte"]$Mean-3*kv_all$SD]
print(excluded_duration_for)
```

#### Piano
```{r outlier_pia, echo = FALSE}
# for piano
excluded_duration_pia <- kv[Subcomponent == "Piano" & Mean < kv_all[Subcomponent == "Piano"]$Mean+3*kv_all[Subcomponent == "Piano"]$SD & Mean > kv_all[Subcomponent == "Piano"]$Mean-3*kv_all$SD]
print(excluded_duration_pia)
```

>>>>

---
title: 'KV Analysis for Performing-Dynamics performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of performing performance (KV) from teaching-v2.0.

@@

#### All
```{r kv_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_kv$TrialNr <- as.factor(dt_kv$TrialNr)
kv_seq <- dt_kv[Subcomponent != "NA", .(N = length(Velocity), Mean = mean(Velocity)), .(SubNr, TrialNr, RowNr)]

p_kv_seq <- ggplot(data = kv_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Velocity", subtitle = "KV: Performing-Dynamics(All)") +
  scale_x_continuous(breaks=seq(1,72,1))
p_kv_seq
```

@@

p_kv_seq_for <- ggplot(data = kv_seq_for, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Key Velocity") + scale_x_continuous(breaks=seq(1,72,1))
p_kv_seq_for
```

@@

p_kv_seq_pia <- ggplot(data = kv_seq_pia, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Key Velocity") + scale_x_continuous(breaks=seq(1,72,1))
p_kv_seq_pia
```

@@

#### Forte
```{r kv_dis_for, fig.width = 14, fig.height = 8, echo = FALSE}
p_kv_dis_for <- ggplot(dt_kv[Subcomponent == "Forte"], aes(x = Velocity)) +
  geom_histogram(binwidth = 2, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Key Velocity", y = "Count", subtitle = "KV: Performing-Dynamics(Forte)")
p_kv_dis_for
```

#### Piano
```{r kv_dis_pia, fig.width = 14, fig.height = 8, echo = FALSE}
p_kv_dis_pia <- ggplot(dt_kv[Subcomponent == "Piano"], aes(x = Velocity)) +
  geom_histogram(binwidth = 2, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Key Velocity", y = "Count", subtitle = "KV: Performing-Dynamics(Piano)")
p_kv_dis_pia
```

@@

### Valid performances (exclude outliers)
#### Forte
```{r outlier_for, echo = FALSE}
# for forte
excluded_kv_for <- kv[Subcomponent == "Forte" & Mean < kv_all[Subcomponent == "Forte"]$Mean+3*kv_all[Subcomponent == "Forte"]$SD & Mean > kv_all[Subcomponent == "Forte"]$Mean-3*kv_all$SD]
print(excluded_kv_for)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Forte"]$N-nrow(excluded_kv_for)`

#### Piano
```{r outlier_pia, echo = FALSE}
# for piano
excluded_kv_pia <- kv[Subcomponent == "Piano" & Mean < kv_all[Subcomponent == "Piano"]$Mean+3*kv_all[Subcomponent == "Piano"]$SD & Mean > kv_all[Subcomponent == "Piano"]$Mean-3*kv_all$SD]
print(excluded_kv_pia)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Piano"]$N-nrow(excluded_kv_pia)`

```{r export, include = FALSE}
kv_valid <- dt_kv[, .(N = length(Velocity), Mean = mean(Velocity)), .(SubNr, TrialNr)]
fwrite(kv_valid, "./kv_valid.csv")
```
